---
title: "Student Sit In"
author: "Mitzy Contreras"
date: "10/28/2019"
output: 
  html_document:
    toc: true
    number_sectons: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ONE SHOT assignment!
this is an extra credit assignment, must be completed Monday Oct 28, turn-in closes at midnight!

## Problem statement: 
Students at UCD- is there a relation between where one sits and one's major? 

## Introduction  

<!-- where is the data found?  Is this an experiment or an observational study?  !-->

Data for this study came from UC Davis with multiple variables out of 173 students. 



```{r include=FALSE, echo=FALSE}
library(tigerstats)
data(ucdavis1)

```

$H_0$: there is no relationship between one's major and where one sits in a class   
$H_A$: where one sits in class and one's major are related  

<!-- Get the data: !-->

names of the data in the data frame

```{r echo=FALSE}
UCDdataframe = data.frame(seat=ucdavis1$Seat, major=ucdavis1$class, data=ucdavis1)
names(UCDdataframe)
```
## Methods

<!--  describe analysis methods here 
what are the variable types, and indicate gaphical, numerical, and inferential methods appropriate
for this question  !--> 
We will use graphical barcharts, numerical, and inferential methods to find the p-value and to find out if there's any relation between where one sits and one's major. 

## Data summary

**Graphical summary**
put the graphic description of the data here

```{r}

barchartGC(~seat+major, data=UCDdataframe, main='seat related to Major', type='percent', xlab='seat')
```

Explain what the graph shows  

The graphical barchart shows that more Liberal Arts students prefer to sit in the front while non Liberal Arts students seem to prefer the back but can almost equally prefer to sit in the middle and or front of the classroom. 

**Numerical summary**  
  
The numerical summary suggests there is not much of a difference between seat preferance and majors.

```{r}
tab1 = xtabs(~seat+major, data=UCDdataframe)
rowPerc(tab1)
```

Explain what the numeric summary says

## Inferential Results
put the inferential test for the the null hypothesis here

```{r}
chisqtestGC(tab1)
```

what is the p-value?  

The P-value is 0.2173 > 0.05, suggesting there is no relationship between where one chooses to sit and one's major. 

## Results and conclusions

<!-- explain-- is there evidence that certain majors tend to sit in particular areas of the class?  Can the results of this test be generalized to all majors in all universities? !-->

explain the result, can the result be generalized?  
  
There is no evidence that one's major and one's seat choice have any correlation. Therefor we fail to reject the null hypothesis. The test can not be generalized between all universities and all majors.
<!--
push results to your github account, turn in the URL

--OR--

If you did not fork my repo to your github account,
create a repository in your github account for this project, get the URL for that repo and 
(in the terminal window..)

$git remote add origin URL_of_your_github_repo
$git push -u origin master

!-->